---
title: "data-output-description"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{data-output-description}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(trisk.model)
library(magrittr)
```

# Obtain outputs 

## Load the test data

Load the internal datasets

```{r}
assets_testdata <- read.csv(system.file("testdata", "assets_testdata.csv", package = "trisk.model"))
scenarios_testdata <- read.csv(system.file("testdata", "scenarios_testdata.csv", package = "trisk.model"))
financial_features_testdata <- read.csv(system.file("testdata", "financial_features_testdata.csv", package = "trisk.model"))
ngfs_carbon_price_testdata <- read.csv(system.file("testdata", "ngfs_carbon_price_testdata.csv", package = "trisk.model"))
```

Define the scenarios to use

```{r}
baseline_scenario <- "NGFS2023GCAM_CP"
target_scenario <- "NGFS2023GCAM_NZ2050"
scenario_geography <- "Global"
```

## Generate outputs
Run the model with the provided data
```{r}
start_time <- Sys.time() # Measure execution time
st_results <- run_trisk_model(
  assets_data = assets_testdata,
  scenarios_data = scenarios_testdata,
  financial_data = financial_features_testdata,
  carbon_data = ngfs_carbon_price_testdata,
  baseline_scenario = baseline_scenario,
  target_scenario = target_scenario,
  scenario_geography = scenario_geography
)
end_time <- Sys.time() # End time
```

```{r}
time_taken <- end_time - start_time
print(paste("Done in ", time_taken))
```

Get result dataframes from function output

```{r}
npv_results <- st_results$npv_results
pd_results <- st_results$pd_results
company_trajectories <- st_results$company_trajectories
```

---

### NPV results

#### Data Description

The `npv_results` dataset includes the following columns:

- `run_id`: Unique identifier for the simulation run.
- `company_id`: Unique identifier for the company.
- `asset_id`: Unique identifier for the asset.
- `company_name`: Name of the company.
- `asset_name`: Name of the asset.
- `sector`: Sector in which the company operates (e.g., Oil&Gas, Coal, Power).
- `technology`: Type of technology used by the company (e.g., Gas, CoalCap, RenewablesCap).
- `net_present_value_baseline`: Net present value (NPV) under the baseline scenario.
- `net_present_value_shock`: Net present value (NPV) under the shock scenario.

#### Data Structure

```{r}
str(npv_results)
```

#### Sample Data

```{r}
knitr::kable(head(as.data.frame(npv_results))) %>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed")) %>%
  kableExtra::scroll_box(width = "100%", height = "400px")
```



### PD results

#### Data Description

The `pd_results` dataset includes the following columns:

- `run_id`: Unique identifier for the simulation run.
- `company_id`: Unique identifier for the company.
- `company_name`: Name of the company.
- `sector`: Sector in which the company operates (e.g., Oil&Gas, Coal).
- `term`: Time period for the probability of default (PD) calculation.
- `pd_baseline`: Probability of default (PD) under the baseline scenario.
- `pd_shock`: Probability of default (PD) under the shock scenario.


#### Data Structure

```{r}
str(pd_results)
```

#### Sample Data

```{r}
knitr::kable(head(as.data.frame(pd_results))) %>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed")) %>%
  kableExtra::scroll_box(width = "100%", height = "400px")
```



### Company trajectories results

#### Data Description

The `company_trajectories` dataset includes the following columns:

- `run_id`: Unique identifier for the simulation run.
- `asset_id`: Unique identifier for the asset.
- `asset_name`: Name of the asset.
- `company_id`: Unique identifier for the company.
- `company_name`: Name of the company.
- `year`: Year of the scenario data.
- `sector`: Sector in which the company operates (e.g., Oil&Gas, Coal).
- `technology`: Type of technology used by the company.
- `production_plan_company_technology`: Production plan for the company’s technology.
- `production_baseline_scenario`: Production output under the baseline scenario.
- `production_target_scenario`: Production output under the target scenario.
- `production_shock_scenario`: Production output under the shock scenario.
- `pd`: Probability of default for the company.
- `net_profit_margin`: Net profit margin for the company.
- `debt_equity_ratio`: Debt to equity ratio for the company.
- `volatility`: Volatility of the company’s asset values.
- `scenario_price_baseline`: Price under the baseline scenario.
- `price_shock_scenario`: Price under the shock scenario.
- `net_profits_baseline_scenario`: Net profits under the baseline scenario.
- `net_profits_shock_scenario`: Net profits under the shock scenario.
- `discounted_net_profits_baseline_scenario`: Discounted net profits under the baseline scenario.
- `discounted_net_profits_shock_scenario`: Discounted net profits under the shock scenario.

#### Data Structure

```{r}
str(company_trajectories)
```

#### Sample Data

```{r}
knitr::kable(head(as.data.frame(company_trajectories))) %>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed")) %>%
  kableExtra::scroll_box(width = "100%", height = "400px")
```

