---
title: "trisk-run-from-folder"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{trisk-run-from-folder}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

``` {r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  echo = FALSE # This hides code execution but shows results
)
```

``` {r, setup, echo=FALSE}
# Load necessary libraries
library(trisk.model)
library(fs)  # For file system operations like copying

# Define source and destination directories
source_dir <- system.file("testdata", package = "trisk.model")
destination_dir <- "./trisk_inputs"

# Create destination directory if it doesn't exist
if (!dir_exists(destination_dir)) {
  dir_create(destination_dir)
}

# Define the files to be copied and their new names
files_to_copy <- c("assets_testdata.csv", "financial_features_testdata.csv", 
                   "ngfs_carbon_price_testdata.csv", "scenarios_testdata.csv")

new_names <- c("assets.csv", "financial_features.csv", 
               "ngfs_carbon_price.csv", "scenarios.csv")

# Loop through the files, copy them, and rename
for (i in seq_along(files_to_copy)) {
  # Construct full file paths
  source_file <- file.path(source_dir, files_to_copy[i])
  destination_file <- file.path(destination_dir, new_names[i])
  
  # Copy the file to the new location with the new name
  file_copy(source_file, destination_file, overwrite = TRUE)
}

# Print a message to indicate the operation is complete
cat("Files have been copied and renamed in ./trisk_inputs.\n")
```

# Input folder structure
The files inside the `trisk_inputs` folder are now structured as follows:

``` {r}
dir_tree(destination_dir)
```

# Generate outputs using the Trisk model

``` {r}
# Define the scenarios to use
baseline_scenario <- "NGFS2023GCAM_CP"
target_scenario <- "NGFS2023GCAM_NZ2050"
scenario_geography <- "Global"
```

``` {r}
# Run the model with the provided data
saved_path <- run_trisk(
  input_path = "./trisk_inputs",
  output_path = "./trisk_outputs",
  baseline_scenario = baseline_scenario,
  target_scenario = target_scenario,
  scenario_geography = scenario_geography
)
```

# Output folder structure
The generated outputs are saved in the `trisk_outputs` folder, structured as:

``` {r}
dir_tree("./trisk_outputs")
```
Each new run generates a folder with a unique name. The folders are named following this convention : DATE_TIME__RUNID

The full path of the run is :

``` {r}
# Print the normalized path to the saved output files
print(normalizePath(saved_path, mustWork = FALSE))
```
