---
title: "trisk-run-from-folder"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{trisk-run-from-folder}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

``` {r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  echo = FALSE # This hides code execution but shows results
)
```

``` {r, setup}
library(trisk.model)
trisk_input_dir <- file.path(".", "trisk_inputs")
trisk_output_dir <- file.path(".", "trisk_outputs")
```

``` {r, echo=FALSE}
library(fs) # For file system operations like copying

# Define source and destination directories
source_dir <- system.file("testdata", package = "trisk.model")

# Create destination directory if it doesn't exist
if (!dir_exists(trisk_input_dir)) {
  dir_create(trisk_input_dir)
}

# Define the files to be copied and their new names
files_to_copy <- c(
  "assets_testdata.csv", "financial_features_testdata.csv",
  "ngfs_carbon_price_testdata.csv", "scenarios_testdata.csv"
)

new_names <- c(
  "assets.csv", "financial_features.csv",
  "ngfs_carbon_price.csv", "scenarios.csv"
)

# Loop through the files, copy them, and rename
for (i in seq_along(files_to_copy)) {
  # Construct full file paths
  source_file <- file.path(source_dir, files_to_copy[i])
  destination_file <- file.path(trisk_input_dir, new_names[i])
  # Copy the file to the new location with the new name
  file_copy(source_file, destination_file, overwrite = TRUE)
}

# Print a message to indicate the operation is complete
cat("Files have been copied and renamed in ./trisk_inputs.\n")
```

# Input folder structure
The files inside the `trisk_inputs` folder are now structured as follows:

``` {r, echo=TRUE}
dir_tree(trisk_input_dir)
```

# Generate outputs using the Trisk model

``` {r, echo=TRUE}
# Define the scenarios to use
baseline_scenario <- "NGFS2023GCAM_CP"
target_scenario <- "NGFS2023GCAM_NZ2050"
scenario_geography <- "Global"
```

Run the model with the downloaded data :

``` {r, echo=TRUE}
saved_path <- run_trisk(
  input_path = trisk_input_dir,
  output_path = trisk_output_dir,
  baseline_scenario = baseline_scenario,
  target_scenario = target_scenario,
  scenario_geography = scenario_geography
)
```

Results are saved in this folder :
```{r}
print(saved_path)
```

# Output folder structure
The generated outputs are saved in the `trisk_outputs` folder, structured as:

``` {r, echo=TRUE}
dir_tree(trisk_output_dir)
```
Each new run generates a folder with a unique name. The folders are named following this convention : DATE_TIME__RUNID

The normalized path where are saved output files is:

``` {r, echo=TRUE}
print(normalizePath(saved_path, mustWork = FALSE))
```
